\section{Test Plan}

\subsection{Objectives}
\begin{itemize}
    \item Ensure accurate weather data retrieval and alert generation.
    \item Validate reliable data flow across APIs, MQTT topics, and the database.
\end{itemize}

\subsection{Scopes}
\begin{itemize}
    \item Node-RED logic for HTTP fetch, alert logic, and MQTT publishing.
    \item OpenWeather API interaction.
    \item MQTT communication (zzw/iot/alarm, zzw/iot/weather).
    \item InfluxDB write operations.
\end{itemize}

\subsection{Test Types}
\begin{itemize}
    \item Weather Data Fetching: Node-RED fetches from OpenWeather at scheduled intervals via HTTP.
    \item InfluxDB Integration: Data is correctly written to InfluxDB with valid timestamps and fields.
    \item Alert Generation: High/low temperature or rain day triggers correctly detect conditions from forecast data.
    \item Weather Data Publishing: Current and forecast weather data is processed and published to zzw/iot/weather.
    \item End-to-End Data Flow: Verify full pipeline: API → Node-RED → MQTT/InfluxDB; Confirm output matches input (e.g. temperature values and timestamps).
\end{itemize}

\subsection{Entry Criteria}
\begin{itemize}
    \item Node-RED flows deployed.
    \item OpenWeather API key configured.
    \item OpenWeather API key configured.
    \item InfluxDB instance running.
\end{itemize}

\subsection{Exit Criteria}
\begin{itemize}
    \item All functional and API paths tested.
    \item System demonstrates stable data flow and correct alert behavior.
\end{itemize}

